---
title: "CopyNumberPlots: create copy-number specific plots using karyoploteR "
author: "Bernat Gel (bgel@igtp.cat);Miriam Magallon (mmagallon@igtp.cat)"
date: "`r doc_date()`"
package: "`r pkg_ver('CopyNumberPlots')`"
output: 
  BiocStyle::html_document:
    toc: true
vignette: >
  %\VignetteIndexEntry{CopyNumberPlots vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}  
---


```{r, include=FALSE}
library(knitr)
library(CopyNumberPlots)
opts_chunk$set(concordance=FALSE)
set.seed(21666641)
```


# Introduction

Data visualisation is a powerful tool used for data analysis and exploration in 
many fields. Genomics data analysis is one of these fields where good 
visualisation tools can be of great help. 
The aim of `r BiocStyle::Biocpkg("CopyNumberPlots")` is to offer the user an easy way to create 
copy-number related plots using the infrastructure provided by the R package
`r BiocStyle::Biocpkg("karyoploteR")`.

In addition to a set of specialized plotting functions for copy-number analysis
data and results (`plotBAF`, `plotCopyNumberCalls`, ...), 
`r BiocStyle::Biocpkg("CopyNumberPlots")` contains a number of data loading 
functions to help parsing and loading the results of widely used 
copy-number calling software such as `r BiocStyle::Biocpkg("DNAcopy")`, 
[DECoN](https://wellcomeopenresearch.org/articles/1-20/v1) or
[CNVkit](https://cnvkit.readthedocs.io/en/stable/).

Finally, since `r BiocStyle::Biocpkg("CopyNumberPlots")` extends the 
functionality of `r BiocStyle::Biocpkg("karyoploteR")`, it is possible 
to combine the plotting functions of both packages to get the perfect
figure for your data.

# Quick Start



```{r}
  gains <- toGRanges(data.frame(chr=c("chr1", "chr5", "chr17", "chr22"), start=c(1, 1000000, 4000000, 1),
                      end=c(5000000, 3200000, 80000000, 1200000)))
  losses <- toGRanges(data.frame(chr=c("chr3", "chr9", "chr17"), start=c(80000000, 20000000, 1),
                       end=c(170000000, 30000000, 25000000)))
  kp <- plotKaryotype(genome="hg19")
  kpPlotRegions(kp, gains, col="#FFAACC")
  kpPlotRegions(kp, losses, col="#CCFFAA")

```

# Session Info

```{r, sessionInfo}
sessionInfo()
```


